Drivers of spatial synchrony in giant kelp populations

### 2021-05-05 paper/SupMat.Rnw
editted

\noindent for species $i=1,2$. Here, $N_i(t)$ is the population density of species $i$ at time $t$, and $N = N_1(t)+N_2(t)$ is fixed through time. The parameter, $\delta$ is a mortality rate, and $B_i(t)$ is the fecundiity of specise $i$ at time $t$. The model postulates that individuals die at rate $\delta$ at each time step, and are replaced by juveniles in population to the reproductive output of the two species that year. We take, for each $i$, $B_i(t)$ to be $iid$ through time. We let $B_i = exp(b_i)$, where $(b_1, b_2)$ is some distribution such that $b_i \sim N(\mu_i, \sigma^2)$ and such that $cov(b_1, b_2) = \rho$, a fixed quantity we will specify later. However, $(b_1, b_2)$ is not necessarily a bivariate normal distribution. We will consider various distributions of $(b_1, b_2)$ with these properties, corresponding to our symmetric and asymmetric tail associations cases defined in the main text and elaborated below. We assume without loss of generality that $\mu_1 \leq \mu_2$, so that species 1 is the weaker competitor.

@@

\begin{equation}
\bar r_1=\EX(\ln [(1-\delta)+\delta exp(b_1-b_2)]).  \label{rbar1_E}
\end{equation}

@@

\begin{equation}
\bar r_1^\#=\EX(\ln [(1-\delta)+\delta exp(b_1^\#-b_2)]),  \label{rbar1sharp_E}
\end{equation}

@@

\begin{equation}
\bar r_2^\#=\EX(\ln [(1-\delta)+\delta exp(b_2^\#-b_2)]),  \label{rbar2sharp_E}
\end{equation}

@@

\begin{equation}
\bar r_1^\#=\EX(\ln [(1-\delta)+\delta exp(u)]),  \label{rbar1sharp_E_usub}
\end{equation}

@@

\begin{equation}
\bar r_2^\#=\EX(\ln [(1-\delta)+\delta exp(u)]),  \label{rbar2sharp_E_usub}
\end{equation}

@@

\begin{equation}
(b_1,b_2) \sim  N(\begin{pmatrix} \mu_2\\\mu_2\end{pmatrix}, \Sigma) \label{b1b2_distribution_sym}
\end{equation}

@@

Equations \ref{sym_rbar1} - \ref{sym_rbar2sharp} obviously depend only on $\mu_1-\mu_2$, and not independently on $\mu_1$ and $\mu_2$, since only $\mu_1-\mu_2$ appears in these expressions if $\mu_1$ or $\mu_2$ appear at all. Equation \ref{sym_rbar1} is $\bar r_1$ in the asymmetric? tail association cases. But letting $\beta_1 = b_1 + \eta$ and $\beta_2 = b_2 + \eta$ and substituting into \ref{sym_rbar1}, we get

>>>>

\noindent for species $i=1,2$. Here, $N_i(t)$ is the population density of species $i$ at time $t$, and $N = N_1(t)+N_2(t)$ is fixed through time. The parameter, $\delta$ is a mortality rate, and $B_i(t)$ is the fecundiity of specise $i$ at time $t$. The model postulates that individuals die at rate $\delta$ at each time step, and are replaced by juveniles in population to the reproductive output of the two species that year. We take, for each $i$, $B_i(t)$ to be $iid$ through time. We let $B_i = \exp(b_i)$, where $(b_1, b_2)$ is some distribution such that $b_i \sim N(\mu_i, \sigma^2)$ and such that $cov(b_1, b_2) = \rho$, a fixed quantity we will specify later. However, $(b_1, b_2)$ is not necessarily a bivariate normal distribution. We will consider various distributions of $(b_1, b_2)$ with these properties, corresponding to our symmetric and asymmetric tail associations cases defined in the main text and elaborated below. We assume without loss of generality that $\mu_1 \leq \mu_2$, so that species 1 is the weaker competitor.

@@

\begin{equation}
\bar r_1=\EX(\ln [(1-\delta)+\delta \exp(b_1-b_2)]).  \label{rbar1_E}
\end{equation}

@@

\begin{equation}
\bar r_1^\#=\EX(\ln [(1-\delta)+\delta \exp(b_1^\#-b_2)]),  \label{rbar1sharp_E}
\end{equation}

@@

\begin{equation}
\bar r_2^\#=\EX(\ln [(1-\delta)+\delta \exp(b_2^\#-b_2)]),  \label{rbar2sharp_E}
\end{equation}

@@

\begin{equation}
\bar r_1^\#=\EX(\ln [(1-\delta)+\delta \exp(u)]),  \label{rbar1sharp_E_usub}
\end{equation}

@@

\begin{equation}
\bar r_2^\#=\EX(\ln [(1-\delta)+\delta \exp(u)]),  \label{rbar2sharp_E_usub}
\end{equation}

@@

\begin{equation}
(b_1,b_2) \sim  N(\begin{pmatrix} \mu_1\\\mu_2\end{pmatrix}, \Sigma) \label{b1b2_distribution_sym}
\end{equation}

@@

Equations \ref{sym_rbar1} - \ref{sym_rbar2sharp} obviously depend only on $\mu_1-\mu_2$, and not independently on $\mu_1$ and $\mu_2$, since only $\mu_1-\mu_2$ appears in these expressions if $\mu_1$ or $\mu_2$ appear at all. Equation \ref{sym_rbar1} is $\bar r_1$ in the asymmetric? tail association cases. But letting $\beta_1 = b_1 + \eta$ and $\beta_2 = b_2 + \eta$ and substituting into \ref{rbar1_E}, we get
